Species richness and food-web structure jointly drive community biomass and its temporal stability in fish communities

### 2021-07-06 manuscript/bef_stability/manuscript.Rmd
A proposition for reviewer 3

In our study system, the destabilising effect of species richness via increased
population variability was stronger than the stabilising effect via decreased
synchrony. The balance between both effects is governed by the balance in the
variation in population variability and synchrony among communities, this
because we used standardised coefficients (see methods). Such an effect of
population variability on community stability twice as strong as the one of
synchrony is expected from the mathematical relation between these three
variables. This indicates that the variability of population variability and
synchrony among the studied communities are equivalent (Eq. \@ref(eq:stab)).
This result contrasts with previous findings on terrestrial animal communities
showing a variability in population synchrony twice as strong as the one of
population variability [@olivier_urbanization_2020]. Such difference in the
relative variability of population stability and synchrony between studies might
be related to the multitrophic structure of the dataset as theory predicts
potential synchronising effect of generalist predators, such as piscivorous
fishes, on prey dynamics [@raimondo_interspecific_2004; @huber_role_2006].
Trophic interactions might also raise synchrony between predators and preys and
thereby increase the overall synchrony of trophic communities [Fig. S9,
@bulmer_phase_1975]. However, generalist predators can also generate
asynchronous dynamics among preys depending on the distribution of interaction
strengths [@huber_role_2006; @mccann_more_2009]. The difference between our
results and those of @olivier_urbanization_2020 might also relate to the type of
ecosystems considered. Aquatic ecosystems have been suggested to show greater
population variability than terrestrial ecosystems [@rip_cross-ecosystem_2011],
which could also translate in greater variation range of population variability
among aquatic communities than among terrestrial ones. Another hypothesis
relates to the evenness of the biomass distribution among species, with low
evenness decreasing the range of variation in synchrony among communities and thereby
the strength of the portfolio effect [@doak_statistical_1998;
@thibaut_understanding_2013]. Whether the biomass distribution in stream fish
assemblages is particularly uneven when compared to the terrestrial communities
studied by @olivier_urbanization_2020 remains however to be tested. In any case,
more studies are needed to understand how the relative importance of synchrony
and population variability for community stability varies among ecosystems.

>>>>

In our study system, the destabilising effect of species richness via increased
population variability was stronger than the stabilising effect via decreased
synchrony.  This contrasts with the previous study of Olivier et al. (2021) on
animal communities in terrestrial ecosystems. The difference of the effect of
species richness on population stability and synchrony between studies might be
related to the multitrophic structure of the dataset as theory predicts
potential synchronising effect of generalist predators, such as piscivorous
fishes, on prey dynamics [@raimondo_interspecific_2004; @huber_role_2006].
Trophic interactions might also raise synchrony between predators and preys and
thereby increase the overall synchrony of trophic communities [Fig. S9,
@bulmer_phase_1975]. However, generalist predators can also generate
asynchronous dynamics among preys depending on the distribution of interaction
strengths [@huber_role_2006; @mccann_more_2009]. The difference between our
results and those of @olivier_urbanization_2020 might also relate to the type of
ecosystems considered. Aquatic ecosystems have been suggested to show greater
population variability than terrestrial ecosystems [@rip_cross-ecosystem_2011],
which could also translate in greater variation range of population variability
among aquatic communities than among terrestrial ones. Another hypothesis
relates to the evenness of the biomass distribution among species, with low
evenness decreasing the range of variation in synchrony among communities and
thereby the strength of the portfolio effect [@doak_statistical_1998;
@thibaut_understanding_2013]. Whether the biomass distribution in stream fish
assemblages is particularly uneven when compared to the terrestrial communities
studied by @olivier_urbanization_2020 remains however to be tested. In any case,
more studies are needed to understand how the relative importance of the effect
of species richness on synchrony and population variability varies among
ecosystems.
